Object-Oriented Internet - Azure Interoperability

### 2020-11-14 Latex/Manuscript.tex
Work out Markdown\60.GatewayImplementation.md #35
- integrate with other sections - working copy

The remainder of this paper is structured as follows. Sect.~\ref*{cloud-to-sensors-field-level-connectivity} presents the proposed open and reusable software model. It promotes a reactive interoperability pattern and a generic approach to establishing interoperability-context. A reference implementation of this archetype is described in Sect.~\ref*{sect.gateway-implementation}. The most important findings and future work are summarized in Sect.~\ref*{conclusion}.

@@

\subsection{Architecture}\label{architecture}

@@

\begin{figure}
      \centering
      \includegraphics{../.Media/StrategyDomainModel.png}
      \caption{Strategy Domain Model}\label{StrategyDomainModel}
\end{figure}

Unlike the above described solutions, the \textbf{embedded gateway} is not derived from the middleware concept. The domain model for this archetype is presented in the Fig.~\ref*{StrategyDomainModel}. Promoting separation of concern design principle, the gateway functionality should be implemented as a self-contained software part embedded in the \textit{Networking} service of the \textit{Cyber-physical\ node}. Main functionality of this component is to transfer selected data between \textit{Cyber-physical\ network} using \textit{Networking} services of an existing \textit{Cyber-physical\ node} and \textit{Cloud-based\ front-end} using officially supported by the cloud vendor interconnection services.

The \textbf{embedded gateway} archetype relaxes most of the issues described above: \textit{Cyber-physical\ network} real-time behavior, data encoding incompatibility, security-context differences to name only a few. The main goal of this article is to provide proof that the \textbf{embedded gateway} archetype implementation is possible based on a generic architecture that can be used as a foundation for the integration of the heterogenous environments in concern. The proposed implementation is designed for selected interoperability standard and cloud product.

@@

Based on the sessionless and session-oriented communication patterns examination against the IoT requirements \cite{mpostol2020} it could be concluded that the connectionless pattern better suites issues related to the assets mobility and traffic asymmetry that is characteristic for the application domains in concern. Additionally, to promote interoperability and address the demands of the M2M communication in the context of a multi-vendor environment the prototyping should use a framework that must be compliant with the OPC UA Part 14 PubSub spec \cite{RefWorks:doc:5d98837de4b055984c0eecf0}. According to proposed architecture (Fig.~\ref*{StrategyDomainModel}) to implement the \textit{Embedded\ Gateway} as a composable part of the \textit{Cyber-physical\ Node} a library implementing \textit{Networking} functionality in compliance with mentioned above specification is a starting point for further development. Additionally it must be assumed that the library used to deploy \textit{Embedded\ Gateway} support dependency injection and be capable to compose an external part supporting Azure/pubsub gateway functionality. The composition process must be available without modification of the core code of an existing library. As a result the prototyping is to be limited to implementation of the \textit{Embedded\ Gateway} software part only.

@@

To promote interoperability and address the demands of the M2M communication in the context of a multi-vendor environment the prototyping should use a framework that must be compliant with the OPC UA Part 14 PubSub (Sect. \ref*{architecture}) and support the \emph{Reactive Interoperability} (Sect. \ref*{introduction}) concept. A framework compliant with this requirements has been implemented as an open-source library named \textit{UAOOI.Networking.SemanticData} (SDK) under an umbrella of the project Object-Oriented Internet \cite{RefWorks:doc:5c66740ae4b081adf5804596}. The library is designed to be a foundation for developing application programs that are taking part in a message-centric communication pattern and interconnected using the reactive networking concept. The diagram in Fig.~\ref*{UADataApplicationArchitecture} shows the relationship between the library \textit{SDK} and external parts composing any reactive networking application (\textit{Reactive\ Application}). The \textit{Reactive Application} is an aggregation of \textit{Producer} and \textit{Consumer} parts. They must support access to real-time process data, hence they are recognized as an extension of \textit{DataRepository} class. To implement the \textit{DataRepository} dedicated implementation of the \textit{IBinding} interface should be provided to create a bridge between CPS and an external row data represented by the \textit{LocalResources} class. A more in-depth description of the \textit{OOI Reactive Application} library enabling data exchange over a network using the reactive networking pattern is in \cite{mpostol2020}.

\begin{figure}
      \centering
      \includegraphics[width=5cm]{../.Media/UADataApplicationArchitecture.png}
      \caption{Reactive interoperability implementation}\label{UADataApplicationArchitecture}
\end{figure}

@@

Piece by piece integration of a cyber-physical system using multi-vendor products requires that M2M communication employs international standards as the interoperability foundation. OPC Unified Architecture Part 14 PubSub has been selected in this respect (Sect. \ref*{architecture}). By design, this standard should support the required publisher-subscriber communication pattern. It must be stressed, that by design, the specification provides only an abstract interoperability definition. Abstract means that the standard must not limit the implementation strategy.

Many parts in the domain model presented in Fig.~\ref*{UADataApplicationArchitecture} requires a polymorphic approach to implementation. To promote the polymorphic ready solution the following concepts have been adopted:

@@

The \textit{Consumer} and \textit{Producer} classes are derived from the \textit{DataRepository} (Fig.~\ref*{UADataApplicationArchitecture}). The \textit{Consumer} uses the \textit{IBindingFactory} to gather the data recovered from the \emph{Message} instances pulled from a network. The received data may be processed or driven to any data destination, e.g. cloud-based front-end. The \textit{Producer} mirrors the \textit{Consumer} functionality and, after reading data from an associated source, populates the \emph{Message} using the gathered data.

@@

From the discussion covered by the Sect. \ref*{architecture} we can infer that the interoperability of communicating parties requires establishing a semantic-context and security-context between them. If the received data is driven to any external data destination (e.g. cloud-based front-end) using out-of-band protocol semantic-context and security context must be defined for this interoperability relationship. There are a vast variety of possibilities for how to define these contexts. Anyway, the most common starting point is the configuration. The proposed approach to instantiate the application as a set of composable parts is very useful in this respect because it makes it possible to expand the core configuration functionality and adapt it to be helpful also in this case. Therefore, the semantic-context may be created based on the configuration using the implementation of the \textit{IConfigurationDataFactory} interface.

@@

\subsection{Preface}\label{preface}

@@

\subsection{Architecture}\label{architecture}

Domain model presenting relationship between the: Azure, PubSub Gateway, Device, Design and development tools

@@

The article provides an introductory understanding of the steps required to implement the \textit{Consumer} role of \textit{OOI\ Reactive\ Application}. The \textit{ReferenceApplication} is an example application of \textit{Semantic-Data} reactive networking based on {[}OPC UA PubSub{]}{[}OPC.UA.PubSub{]} specification. The document {[}OPC UA PubSub Main Technology Features{]}{[}PubSubMTF{]} covers a description of selected fetuses relevant to this specification.

@@

\subsubsection{\texorpdfstring{\textit{DataManagementSetup} implementation}{DataManagementSetup implementation}}\label{datamanagementsetup-implementation}

The \textit{PartDataManagementSetup} constructor initializes all properties, which are injection points of all parts composing this role.

In this example, it is assumed that \href{https://www.nuget.org/packages/CommonServiceLocator}{\textit{ServiceLocator}} is implemented to resolve references to any external services.

@@

\subsubsection{\texorpdfstring{\textit{IBindingFactory} implementation}{IBindingFactory implementation}}\label{ibindingfactory-implementation}

@@

\subsection{Configuration}\label{configuration}

@@

\subsection{Protocol selection}\label{protocol-selection}

From the description covered by the Sec. and the Sec. the Azure supports the HTTP, AMQP, MQTT, but the PubSub Ethernet, UDP, AMQP, MQTT. If the Ethernet or UDP has been selected to build interconnection based on PubSub direc interoperability with the PubSub is impossible because the Azure doesn't offer these protocol as native communication services.

\subsection{data mapping}\label{data-mapping}

@@

\subsection{Security}\label{security}

@@

\subsection{Deployment phases}\label{deployment-phases}

\begin{itemize}
      \item Design
      \item Gateway and devices registration
      \item Authentication
      \item Device/Service association
      \item Device/Application association
      \item Establishing session
            \begin{itemize}
                  \item Device/Device Template (Device Capability Model) association - establishing a semantic-context
                  \item Security management - establishing security-context
            \end{itemize}
      \item Interconnection - exchange of data
      \item Maintenance
\end{itemize}

\section{Conclusion}\label{conclusion}

>>>>

The remainder of this paper is structured as follows. Sect.~\ref*{cloud-to-sensors-field-level-connectivity} presents the proposed open and reusable software model. It promotes a reactive interoperability pattern and a generic approach to establishing interoperability-context. A reference implementation of this archetype is described in Sect.~\ref*{sect.gateway-implementation}. The most important findings and future work are summarized in Sect.~\ref*{section.conclusion}.

@@

\subsection{Architecture}\label{subs.architecture}

@@

\begin{figure}
      \centering
      \includegraphics{../.Media/StrategyDomainModel.png}
      \caption{Strategy Domain Model}\label{figure.StrategyDomainModel}
\end{figure}

Unlike the above described solutions, the \textbf{embedded gateway} is not derived from the middleware concept. The domain model for this archetype is presented in the Fig.~\ref*{subs.architecture}. Promoting separation of concern design principle, the gateway functionality should be implemented as a self-contained software part embedded in the \textit{Networking} service of the \textit{Cyber-physical\ node}. Main functionality of this component is to transfer selected data between \textit{Cyber-physical\ network} using \textit{Networking} services of an existing \textit{Cyber-physical\ node} and \textit{Cloud-based\ front-end} using officially supported by the cloud vendor interconnection services.

The \textbf{embedded gateway} archetype relaxes most of the issues described above: \textit{Cyber-physical\ network} real-time behavior, data encoding incompatibility, security-context differences to name only a few. The main goal of this article is to provide proof that the \textbf{embedded gateway} archetype implementation is possible based on a generic subs.architecture that can be used as a foundation for the integration of the heterogenous environments in concern. The proposed implementation is designed for selected interoperability standard and cloud product.

@@

Based on the sessionless and session-oriented communication patterns examination against the IoT requirements \cite{mpostol2020} it could be concluded that the connectionless pattern better suites issues related to the assets mobility and traffic asymmetry that is characteristic for the application domains in concern. Additionally, to promote interoperability and address the demands of the M2M communication in the context of a multi-vendor environment the prototyping should use a framework that must be compliant with the OPC UA Part 14 PubSub spec \cite{RefWorks:doc:5d98837de4b055984c0eecf0}. According to proposed architecture (Fig.~\ref*{subs.architecture}) to implement the \textit{Embedded\ Gateway} as a composable part of the \textit{Cyber-physical\ Node} a library implementing \textit{Networking} functionality in compliance with mentioned above specification is a starting point for further development. Additionally it must be assumed that the library used to deploy \textit{Embedded\ Gateway} support dependency injection and be capable to compose an external part supporting Azure/pubsub gateway functionality. The composition process must be available without modification of the core code of an existing library. As a result the prototyping is to be limited to implementation of the \textit{Embedded\ Gateway} software part only.

@@

To promote interoperability and address the demands of the M2M communication in the context of a multi-vendor environment the prototyping should use a framework that must be compliant with the OPC UA Part 14 PubSub (Sect. \ref*{subs.architecture}) and support the \emph{Reactive Interoperability} (Sect. \ref*{introduction}) concept. A framework compliant with this requirements has been implemented as an open-source library named \textit{UAOOI.Networking.SemanticData} (SDK) under an umbrella of the project Object-Oriented Internet \cite{RefWorks:doc:5c66740ae4b081adf5804596}. The library is designed to be a foundation for developing application programs that are taking part in a message-centric communication pattern and interconnected using the reactive networking concept. The diagram in Fig.~\ref*{figure.UADataApplicationArchitecture} shows the relationship between the library \textit{SDK} and external parts composing any reactive networking application (\textit{Reactive\ Application}). The \textit{Reactive Application} is an aggregation of \textit{Producer} and \textit{Consumer} parts. They must support access to real-time process data, hence they are recognized as an extension of \textit{DataRepository} class. To implement the \textit{DataRepository} dedicated implementation of the \textit{IBinding} interface should be provided to create a bridge between CPS and an external row data represented by the \textit{LocalResources} class. A more in-depth description of the \textit{OOI Reactive Application} library enabling data exchange over a network using the reactive networking pattern is in \cite{mpostol2020}.

\begin{figure}
      \centering
      \includegraphics[width=5cm]{../.Media/UADataApplicationArchitecture.png}
      \caption{Reactive interoperability implementation}\label{figure.UADataApplicationArchitecture}
\end{figure}

@@

Piece by piece integration of a cyber-physical system using multi-vendor products requires that M2M communication employs international standards as the interoperability foundation. OPC Unified Architecture Part 14 PubSub has been selected in this respect (Sect. \ref*{subs.architecture}). By design, this standard should support the required publisher-subscriber communication pattern. It must be stressed, that by design, the specification provides only an abstract interoperability definition. Abstract means that the standard must not limit the implementation strategy.

Many parts in the domain model presented in Fig.~\ref*{figure.UADataApplicationArchitecture} requires a polymorphic approach to implementation. To promote the polymorphic ready solution the following concepts have been adopted:

@@

The \textit{Consumer} and \textit{Producer} classes are derived from the \textit{DataRepository} (Fig.~\ref*{figure.UADataApplicationArchitecture}). The \textit{Consumer} uses the \textit{IBindingFactory} to gather the data recovered from the \emph{Message} instances pulled from a network. The received data may be processed or driven to any data destination, e.g. cloud-based front-end. The \textit{Producer} mirrors the \textit{Consumer} functionality and, after reading data from an associated source, populates the \emph{Message} using the gathered data.

@@

From the discussion covered by the Sect. \ref*{subs.architecture} we can infer that the interoperability of communicating parties requires establishing a semantic-context and security-context between them. If the received data is driven to any external data destination (e.g. cloud-based front-end) using out-of-band protocol semantic-context and security context must be defined for this interoperability relationship. There are a vast variety of possibilities for how to define these contexts. Anyway, the most common starting point is the configuration. The proposed approach to instantiate the application as a set of composable parts is very useful in this respect because it makes it possible to expand the core configuration functionality and adapt it to be helpful also in this case. Therefore, the semantic-context may be created based on the configuration using the implementation of the \textit{IConfigurationDataFactory} interface.

@@

\subsection{Preface}

@@

\subsection{Architecture}

Domain model presenting relationship between the Azure \textit{Cloud-based\ front-end} and \textit{Cyber-physical\ node} attached to the \textit{Cyber-physical\ node} is presented in Fig. \ref*{} \textit{Cloud-based Front-end} and Cyber-physical node, PubSub Gateway, Device, Design and development tools

@@

The article provides an introductory understanding of the steps required to implement the \textit{Consumer} role of \textit{OOI\ Reactive\ Application}. The \textit{ReferenceApplication} is an example application of \textit{Semantic-Data} reactive networking based on OPC UA PubSub\cite{RefWorks:doc:5d98837de4b055984c0eecf0} \todo{cite OPC UA PubSub Main Technology Features}.

@@

The class \textit{DataManagementSetup} constructor initializes all properties, which are injection points of all parts composing this role.

In this example, it is assumed that \textit{ServiceLocator} \footnote{ \url{https://www.nuget.org/packages/CommonServiceLocator} } is implemented to resolve references to any external services.

@@

@@

\subsection{Configuration}

@@

\subsection{Protocol selection}

The Azure supports the HTTP, AMQP, MQTT (Sec. \ref*{azure-main-technology-features}). On other hand the PubSub supports Ethernet, UDP, AMQP, MQTT {Sect. \ref*{subs.architecture}}. If the Ethernet or UDP has been selected to build interconnection based on PubSub direc interoperability between the Azure and PubSub is impossible because the mentioned protocols are not offered as the native communication services.

\subsection{data mapping}

@@

\subsection{Security}

@@

\subsection{Deployment phases}

\begin{itemize}
      \item Design
      \item Gateway and devices registration
      \item Authentication
      \item Device/Service association
      \item Device/Application association
      \item Establishing session
            \begin{itemize}
                  \item Device/Device Template (Device Capability Model) association - establishing a semantic-context
                  \item Security management - establishing security-context
            \end{itemize}
      \item Interconnection - exchange of data
      \item Communication maintenance
\end{itemize}

\section{Conclusion}\label{section.conclusion}
